Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/high-assurance-contracts.tex
Add minor edits no section 5

BriefCASE creates all the needed AADL for the new high-assurance
component, and its connections in the system implementation, as part
of the transformation.  It also creates a default AGREE specification
that defines everything about the component behavior, leaving only the
component behavior (policy) to be specified.

@@

\subsubsection{Monitor specification}
BriefCASE generates everything but the
\konst{eq}-statements in \linesref{line:mon-assume}{line:mon-policy} of
\figref{fig:monitor}.

The \texttt{alert} variable defined on \lineref{line:mon-alert}
(distinct from the \texttt{Alert} port) depends not just on the policy
but also on configuration details supplied when the component is
specified.  At configuration time, \texttt{is\_latched} has been set
to \konst{true}, thus making the alert persistent, meaning that once
the alert is raised, it is always raised; otherwise, it is the
complement of the policy value in the current step.

The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending} on \lineref{line:mon-pending}, and
counting the number of steps between requests, \texttt{latency} on
\lineref{line:mon-latency}.  The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--\emph{not response since request and not response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one.

The latency bound for the monitor is defined by the constant
\texttt{MAX\_LATENCY} on \lineref{line:mon-const}.  Here the constant
is set to one to be consistent with the system specification from the
previous section.  At time zero the policy is trivial: a response
requires an accompanying request.  After time zero, if a request is
pending in the current time step, then the latency must still be under
the bound, and if there is a response, then it closes a request now or
a pending request from earlier in time.

The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption on
\lineref{line:mon-assume} and is the same assumption used for the
system input.  The policy can be written without the assumption,
but the policy is much simpler to write with the assumption.

As shown in \figref{fig:hardened-certificate}, the cyber-hardened
system passes AGREE verification.  That means that the high-assurance
components protect the WM from the untrusted AI generating malformed
data, spontaneous responses, or delayed responses.  Synthesis must
generate faithful implementations of the high-assurance component
specifications for the AGREE verification result to apply to the
deployed system.

>>>>

BriefCASE creates all the needed AADL for the new high-assurance
component, and its connections in the system implementation, as part
of the transformation.  It also creates a default code contract with
appropriate output guarantees leaving only the component behavior 
(policy) to be specified.

@@

\subsubsection{Monitor specification}
The monitor policy is given by the \konst{eq}-statements in \linesref{line:mon-assume}{line:mon-policy} of
\figref{fig:monitor}.
\lineref{line:mon-alert}. The \texttt{alert} variable
(distinct from the \texttt{Alert} port) depends not just on the policy
but also on configuration details supplied when the component is
specified.  At configuration time, \texttt{is\_latched} has been set
to \konst{true}, thus making the alert persistent, meaning that once
the alert is raised, it is always raised; otherwise, it is the
complement of the policy value in the current step.

\lineref{line:mon-pending} and \lineref{line:mon-latency}.
The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending}, and
counting the number of steps between requests, \texttt{latency}.  
The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--to be read as \emph{there is no response since the most recent request without a corresponding response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one.

\lineref{line:mon-const}. The latency bound for the monitor is defined by the constant
\texttt{MAX\_LATENCY}.  Here the constant
is set to one to be consistent with the system specification from the
previous section.  At time zero the policy is trivial: a response
requires an accompanying request.  After time zero, if a request is
pending in the current time step, then the latency must still be under
the bound, and if there is a response, then it closes a request now or
a pending request from earlier in time.

\lineref{line:mon-assume}. The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption and is the same assumption used for the
system input.  The policy can be written without the assumption,
but the policy is much simpler to write with the assumption.

As shown in \figref{fig:hardened-certificate}, the cyber-hardened
system passes AGREE verification.  That means that the high-assurance
components protect the WM from the untrusted AI generating malformed
data, spontaneous responses, or delayed responses.  Synthesis must
generate faithful implementations of the code contracts for the AGREE verification result to apply to the
deployed system.
